The problem statement has recently been changed. \hyperref[]{View the
changes.}

{×}

A. Cyclic Merging

time limit per test

2 seconds

memory limit per test

256 megabytes

input

standard input

output

standard output

You are given \$\$\$n\$\$\$ non-negative integers
\$\$\$a\_1,a\_2,\textbackslash ldots,a\_n\$\$\$ arranged on a ring. For
each \$\$\$1\textbackslash le i\textless{} n\$\$\$, \$\$\$a\_i\$\$\$ and
\$\$\$a\_\{i+1\}\$\$\$ are adjacent; \$\$\$a\_1\$\$\$ and
\$\$\$a\_n\$\$\$ are adjacent.

You need to perform the following operation {exactly} \$\$\$n-1\$\$\$
times:

\begin{itemize}
\tightlist
\item
  Choose any pair of adjacent elements on the ring, let their values be
  \$\$\$x\$\$\$ and \$\$\$y\$\$\$, and merge them into a single element
  of value \$\$\$\textbackslash max(x,y)\$\$\$ with cost
  \$\$\$\textbackslash max(x,y)\$\$\$.
\end{itemize}

Note that this operation will decrease the size of the ring by
\$\$\$1\$\$\$ and update the adjacent relationships accordingly.

Please calculate the minimum total cost to merge the ring into one
element.

Input

Each test contains multiple test cases. The first line contains the
number of test cases \$\$\$t\$\$\$ (\$\$\$1 \textbackslash le t
\textbackslash le 10\^{}4\$\$\$). The description of the test cases
follows.

The first line of each test case contains an integer \$\$\$n\$\$\$
(\$\$\$2\textbackslash le n\textbackslash le 2\textbackslash cdot
10\^{}5\$\$\$).

The following line contains \$\$\$n\$\$\$ integers
\$\$\$a\_1,a\_2,\textbackslash ldots,a\_n\$\$\$
(\$\$\$0\textbackslash le a\_i \textbackslash le 10\^{}9\$\$\$).

It is guaranteed that the sum of \$\$\$n\$\$\$ over all test cases does
not exceed \$\$\$2\textbackslash cdot 10\^{}5\$\$\$.

Output

For each test case, please print a single integer~--- the minimum total
cost.

Example

Input

\begin{verbatim}
341 1 3 220 271 1 4 5 1 4 1
\end{verbatim}

Output

\begin{verbatim}
6219
\end{verbatim}

Note

In the first test case, we can achieve a cost of \$\$\$6\$\$\$ on
\$\$\${[}1,1,3,2{]}\$\$\$ as follows:

\begin{itemize}
\tightlist
\item
  Merge indexes \$\$\$1\$\$\$ and \$\$\$2\$\$\$ with a cost of
  \$\$\$1\$\$\$, the ring becomes \$\$\${[}1,3,2{]}\$\$\$.
\item
  Merge indexes \$\$\$1\$\$\$ and \$\$\$3\$\$\$ with a cost of
  \$\$\$2\$\$\$, the ring becomes \$\$\${[}3,2{]}\$\$\$.
\item
  Merge indexes \$\$\$1\$\$\$ and \$\$\$2\$\$\$ with a cost of
  \$\$\$3\$\$\$, the ring becomes \$\$\${[}3{]}\$\$\$.
\end{itemize}

The total cost is \$\$\$1+2+3=6\$\$\$. It can be proven that it is
impossible to achieve a lower cost; thus, the answer is indeed
\$\$\$6\$\$\$.

In the second test case, the only option is to merge the two elements,
with a cost of \$\$\$2\$\$\$.
